The paper on \Large \bf Blockchain Frontrunning

### 2018-09-05 frontrunning/Latex/sections/paper.tex
[frontrunning] Notes from the meeting Sep 5

>>>>

\textbf{Note to Change the structure of the paper: to pitch this paper as a case study, we can polish it as a Bancor case study: 1) here is the bancor project that we look at 2) we find that the issue is mostly the frontrunning 3) So we take a deep look into what is frontrunning 4) we find other case studies that are vulnerable and go through each case}
